---
title: "Scatterplot"
author: "Maddie Meltzer"
date: "2/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

https://shiny.rstudio.com/tutorial/written-tutorial/lesson5/

```{r, warning=FALSE, message=FALSE}

library(tidyverse)
library(dplyr)
library(janitor)

```

### Read in data
```{r,  warning=FALSE, message=FALSE}

threatened_species <- read_csv("IUCN_thr_species_data.csv")
population <- read_csv("PopGrowthRate.csv")

```

### Wrangle data to include only total world population (medium variant) & add totals to threatened species
```{r, warning=FALSE, message=FALSE}

worldpop2050 <- population %>% 
  select(Country, Low, Medium, High)

total_species2 <- threatened_species %>% 
  adorn_totals("row")

total_species2$Plants <- NULL
total_species2$Fungi_Protists <- NULL
total_species2$Other_Invertebrates <- NULL
total_species2$Region <- NULL

scatterplot_df <- merge(total_species2, worldpop2050) %>% 
  arrange(Continent)

summary(scatterplot_df)
head(scatterplot_df)

#Assign correct attributes to each column
scatterplot_df$Continent <- as.factor(scatterplot_df$Continent)

write.csv(scatterplot_df, "clean_scatterplot.csv")

```

write.table(df_species_worldpop, "cleaned_scatterplot.txt")

##X axis = total threatened species (or species by class) (Numbers of threatened species (Critically Endangered, Endangered and Vulnerable)
##Y axis = projected population increase to 2050


```{r, warning=FALSE, message=FALSE}

medium <- scatterplot_df$Medium
total <- scatterplot_df$Total


ggplot(scatterplot_df, aes(x = total, y = medium)) +
  geom_point() +
  geom_text(label = scatterplot_df1$Country) +
  labs(x = "Number of Threatened Species", y = "Rate of Population Increase to 2050", 
       title = "Threatened Species and Projected Population Increase") +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "blank", 
        size = 0.5), panel.background = element_rect(fill = "white"))

```

#ggplot(df_species_worldpop, aes(x = df_species_worldpop$Total, y = df_species_worldpop$`2050-2055`)) +
  #geom_point() +
  #geom_text(label = df_species_worldpop$Country) +
  #geom_label_repel(data = df_species_worldpop, aes(label = Country)) +
  #xlab("Total Threatened Species") +
  #ylab("Rate of Population Increase to 2050")

c("Africa", "Asia", "North America", "South America", "Oceania", "Europe")
